---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ggstamp


<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

> 'In God we trust, all others must bring data.' - W. Edwards Deming.

The goal of ggstamp is to provide an alternative, quick API for annotation layers in the ggplot2 and grammar of graphics framework.  It is experimental and maybe is not such a good idea; but let's see where things lead. 

In some ways, *annotation layers* are subject Deming's burden of *'bringing data'*.  

Annotation layers in grammar of graphics frameworks feel different than adding geom_* layers.  This is because w/ the separation of visual concerns, data is often declared separately from the geom.  The data is foundational and sits below everything.  The ink on the page depends on this underlying data once goem_* layers are declared.  

But with annotion layers, not only are you declaring the geom to be used, but you've also got to declare the data as you do this.  







And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("EvaMaeRey/ggstamp")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(ggstamp)
## basic example code
```




There are different approaches to getting this done currently...

```{r}
# knitr::include_url("docs/flipbook.html")
```


