---
title: ggstamp
subtitle: ""
author: "Exploded Examples"
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: [default, hygge, ninjutsu]
    nature:
      ratio: 16:9
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r setup, echo = F}
knitr::opts_chunk$set(echo = TRUE, message = F, warning = F, fig.height = 6, comment = "")
options(knitr.duplicate.label = "allow")
library(ggstamp)
```


---

`r flipbookr::chunk_reveal('ggbackdrop_1', title = '### ggbackdrop')`

```{r ggbackdrop_1, include = F}
library(ggplot2)
ggbackdrop() +
stamp_curve(curvature = .3, yend = 75, xend = 100) +
stamp_polygon(x0 = 20, y0 = 60, radius = 20, alpha = .4) +
stamp_text(x = 20, y = 60, label = "{ggstamp}",
           size = 5, color = "grey97") +
theme_void()
```



---

`r flipbookr::chunk_reveal('ggcanvas_2', title = '### ggcanvas')`

```{r ggcanvas_2, include = F}
library(ggplot2)
ggcanvas() +
  stamp_point(color = "plum4") +
  stamp_point(x = 1, y = 1,
              color = "lightsteelblue3",
              size = 35) +
  stamp_arrow(color = "plum4",
              headlength = .06,
              type = "closed") +
  stamp_label(1.5, 2.5, label = "      nnnnn",
              size = 15,
              fill = "lemonchiffon", ) +
  stamp_bubble(2.5, 1.25, size = 100,
               color = "plum4") +
  stamp_point(x = c(2,2:4), y = 1:4,
              color = "paleturquoise",
              size = 15) +
  stamp_arrow(y = 2, yend = 1:4,
              xend = c(2,2:4),
              color = "cadetblue4") +
  stamp_label(1, 3.5, label = "Stamps!",
              fill = "paleturquoise3") +
  stamp_label(3.2, 1.75, label = "Umm...  n         ",
              size = 18,
              fill = "thistle") +
  stamp_label(3.2, 1.75, label = "Umm...  n Stamps!",
              size = 18,
              fill = "thistle") +
  theme_void() +
  stamp_curve(x = .25 + log(1:12),
              xend = 1.5 + sqrt(1:12),
              y = 0 + 1:12/20,
              color = "palegreen3",
              yend = 1:12/6,
              curvature = -.1,
              alpha = 12:1/12)
```



---

`r flipbookr::chunk_reveal('ggdraft_3', title = '### ggdraft')`

```{r ggdraft_3, include = F}
# remove drafting lines
(ggdraft() +
stamp_polygon(x0 = 20, y0 = 40,
              radius = 20, alpha = .4) +
stamp_polygon(x0 = 85, y0 = 23,
              radius = 22,
              n = 5, fill = "seagreen2")
   ) +
theme_void()
```



---

`r flipbookr::chunk_reveal('ggdraft_4', title = '### ggdraft')`

```{r ggdraft_4, include = F}
library(ggplot2)
ggdraft() +
stamp_curve(curvature = .13,
            size = .09,
            yend = 20:60,
            xend = 100) +
stamp_polygon(x0 = 20, y0 = 40,
              radius = 20, alpha = .4) +
stamp_text(x = 20, y = 40, label = "{ggstamp}",
           size = 6, color = "grey97")
```



---

`r flipbookr::chunk_reveal('honeycomb_x_5', title = '### honeycomb_x')`

```{r honeycomb_x_5, include = F}
honeycomb_x()
honeycomb_x(n = 10, x0 = 5, ncol = 2)
```



---

`r flipbookr::chunk_reveal('honeycomb_y_6', title = '### honeycomb_y')`

```{r honeycomb_y_6, include = F}
honeycomb_y()
ggcanvas() +
 stamp_polygon(x0 = honeycomb_x(),
               y0 = honeycomb_y())
```



---

`r flipbookr::chunk_reveal('honeycomb_7', title = '### honeycomb')`

```{r honeycomb_7, include = F}
# a hive
ggcanvas() +
  stamp_polygon(x0y0 = honeycomb(width = 1.8),
                fill = c("goldenrod3"),
                alpha = .8,
                size = 0)  +
  stamp_polygon(x0y0 = honeycomb(width = 1.8, n = 12)[c(6:9, 11),],
                fill = c("goldenrod4"),
                alpha = .8,
                size = 0) +
  stamp_polygon(x0y0 = honeycomb(width = 1.8, n = 15)[c(10,12:15),],
                fill = c("goldenrod2"),
                alpha = .8,
                size = 0) +
  stamp_png(x0y0 = honeycomb(width = 1.8, n = 15)[c(1,5, 10),])
```



---

`r flipbookr::chunk_reveal('honeycomb_8', title = '### honeycomb')`

```{r honeycomb_8, include = F}
# first example
honeycomb()
ggcanvas() +
 stamp_point(xy = honeycomb()) +
 stamp_polygon(x0y0 = honeycomb(n = 15, ncol = 4),
     alpha = .5) +
 stamp_label(label = 1:15, xy = honeycomb(n = 15, ncol = 4)) +
 stamp_polygon(n = 4,
               x0y0 = honeycomb(n = 15, ncol = 4)[15,],
               fill = "magenta", alpha = .4, radius = sqrt(.75))
```



---

`r flipbookr::chunk_reveal('honeycomb_9', title = '### honeycomb')`

```{r honeycomb_9, include = F}
# get coords for single position
honeycomb(n = 15, ncol = 5)[15,]
honeycomb(n = 15, ncol = 5)[1:4,]
```



---

`r flipbookr::chunk_reveal('spoke_y_10', title = '### spoke_y')`

```{r spoke_y_10, include = F}
spoke_y(n = 6)
ggcanvas() +
stamp_label(label = "hello",
           x = spoke_x(n = 5),
           y = spoke_y(n = 5)) +
stamp_point(x = spoke_x(n = 5, rot = 0),
            y = spoke_y(n = 5, rot = 0))
```



---

`r flipbookr::chunk_reveal('spoke_11', title = '### spoke')`

```{r spoke_11, include = F}
# Using w plotspace
ggcanvas() +
stamp_label(label = c("hi", "bye", "tchao"),
            xy = spoke(n = 3,
            rotation = -.5,
            radius = .5))
```



---

`r flipbookr::chunk_reveal('spoke_12', title = '### spoke')`

```{r spoke_12, include = F}
spoke()
spoke(n = 10)
```



---

`r flipbookr::chunk_reveal('stamp_arrow_13', title = '### stamp_arrow')`

```{r stamp_arrow_13, include = F}
# several arrows
 ggcanvas() +
 stamp_arrow(color = "steelblue") +
 stamp_arrow(x = 1:5, y = 2, xend = 2:6,
 headlength = .04, type = "closed",
 color = "darkred") +
 stamp_arrow(x = .5, xend = 1.5,
 ends = "both", angle = 60)
```



---

`r flipbookr::chunk_reveal('stamp_arrow_14', title = '### stamp_arrow')`

```{r stamp_arrow_14, include = F}
# stamp arrow on plot
library(ggplot2)
ggplot(cars) +
  aes(speed, dist) +
  geom_point() +
  stamp_arrow() +
  stamp_arrow(color = "darkred",
  xend = 15, yend = 75)
```



---

`r flipbookr::chunk_reveal('stamp_bubble_15', title = '### stamp_bubble')`

```{r stamp_bubble_15, include = F}
library(ggplot2)
ggplot(cars) +
 aes(speed, dist) +
 stamp_bubble() +
 stamp_bubble(color = "red", x = 10, y = 100)
ggcanvas() +
 stamp_bubble(color = "green") +
 stamp_bubble(x = 1:5, y = 2, size = 8)
```



---

`r flipbookr::chunk_reveal('stamp_curve_16', title = '### stamp_curve')`

```{r stamp_curve_16, include = F}
# a curve
library(ggplot2)
ggplot(cars) +
 aes(speed, dist) +
 geom_point() +
 stamp_curve(color = "darkred",
 xend = 15, yend = 75)
```



---

`r flipbookr::chunk_reveal('stamp_curve_17', title = '### stamp_curve')`

```{r stamp_curve_17, include = F}
# more curves
ggcanvas() +
 stamp_curve() +
 stamp_curve(color = "green") +
 stamp_curve(x = 1:5, yend = 2, xend = 2:6,
 size = 8, alpha = .5) +
 stamp_point(x = 1:5, y = 0)
```



---

`r flipbookr::chunk_reveal('stamp_ellipse_18', title = '### stamp_ellipse')`

```{r stamp_ellipse_18, include = F}
# an ellipse
library(ggplot2)
ggplot(cars) +
 aes(speed, dist) +
 stamp_ellipse() +
 stamp_ellipse(color = "plum4", x0 = 2, y0 = 3, angle = pi/6)
```



---

`r flipbookr::chunk_reveal('stamp_ellipse_19', title = '### stamp_ellipse')`

```{r stamp_ellipse_19, include = F}
# several
ggcanvas() +
 stamp_ellipse(color = "green") +
 stamp_ellipse(x0 = 1:5, y0 = 2, size = 2)
```



---

`r flipbookr::chunk_reveal('stamp_label_20', title = '### stamp_label')`

```{r stamp_label_20, include = F}
# label on a canvas
ggcanvas() +
   stamp_label()
```



---

`r flipbookr::chunk_reveal('stamp_label_21', title = '### stamp_label')`

```{r stamp_label_21, include = F}
# labels on a plot
library(ggplot2)
ggplot(cars) +
 aes(speed, dist) +
 geom_point() +
 stamp_label(x = 20, y = 10) +
 stamp_label(label = "hi",
 y = c(100, 75, 50), x = 5, fill = "cadetblue2", label.size = 0)
```



---

`r flipbookr::chunk_reveal('stamp_png_22', title = '### stamp_png')`

```{r stamp_png_22, include = F}
# png spokes
ggcanvas() +
  stamp_png()
```



---

`r flipbookr::chunk_reveal('stamp_png_23', title = '### stamp_png')`

```{r stamp_png_23, include = F}
# stamp in plotspace
library(ggplot2)
ggplot(cars, aes(dist, speed)) +
  geom_point() +
  stamp_png(x0 = 5:11*10, y0 = 10,
            height = 1, width = 10) +
  scale_fill_identity()
```



---

`r flipbookr::chunk_reveal('stamp_png_24', title = '### stamp_png')`

```{r stamp_png_24, include = F}
# tiling pngs needs work
ggcanvas() +
  stamp_png(x0y0 = wrap_png(),
  alpha = .75)
```



---

`r flipbookr::chunk_reveal('stamp_png_25', title = '### stamp_png')`

```{r stamp_png_25, include = F}
# two stamps
ggcanvas() +
  stamp_png() +
  stamp_png(x0 = 2:3, y0 = 6,
            width = .95) +
  scale_fill_identity()
```



---

`r flipbookr::chunk_reveal('stamp_point_26', title = '### stamp_point')`

```{r stamp_point_26, include = F}
# more points on canvas
ggcanvas() +
 stamp_point(color = "darkgreen") +
 stamp_point(x = 1:5, y = 2,
             size = 8, alpha = .5) +
 stamp_point(xy = wrap(y0 = -2,
             n = 13, ncol = 4),
             color = "plum") +
 stamp_point(xy = wrap(x0 = 1,
             n = 7, ncol = 4, width = .5))
```



---

`r flipbookr::chunk_reveal('stamp_point_27', title = '### stamp_point')`

```{r stamp_point_27, include = F}
# stamp in plot space
library(ggplot2)
ggplot(cars) +
 aes(speed, dist) +
 geom_point() +
 stamp_point() +
 stamp_point(color = "red", x = 10, y = 100)
```



---

`r flipbookr::chunk_reveal('stamp_polygon_28', title = '### stamp_polygon')`

```{r stamp_polygon_28, include = F}
# lots of polygons
 ggcanvas() +
 stamp_polygon(color = "turquoise4", radius = 3, n = 5, fill = "turquoise") +
 stamp_polygon(fill = "slateblue2", radius = 2, n = 7) +
 stamp_polygon(linetype = "dashed", alpha = .5, fill = "plum2") +
 stamp_polygon(x0 = 1, y0 = 1.5, n = 3, rotation = .25, size = 0,
  fill = "goldenrod2") +
 stamp_polygon(n = 50, radius = .2, size = 0) +
 stamp_spoke(angle = pi * 1:7/15, radius = 2)
```



---

`r flipbookr::chunk_reveal('stamp_polygon_29', title = '### stamp_polygon')`

```{r stamp_polygon_29, include = F}
# on a canvas
 ggcanvas() +
  stamp_polygon(n = 3, x0 = c(0, 2.5),
  fill = "magenta", color = "purple") +
  stamp_label(x = spoke_x(x0 = 0, n = 3),
              y = spoke_y(y0 = 0, n = 3),
              label = c("hi", "hello", "bye")) +
  stamp_point(color = "turquoise")
```



---

`r flipbookr::chunk_reveal('stamp_polygon_30', title = '### stamp_polygon')`

```{r stamp_polygon_30, include = F}
# on plot space
library(ggplot2)
ggplot(cars) +
 aes(speed, dist) +
 geom_point() +
 stamp_polygon(color = "darkred", radius = 5)
```



---

`r flipbookr::chunk_reveal('stamp_polygon_31', title = '### stamp_polygon')`

```{r stamp_polygon_31, include = F}
# some more
 ggcanvas() +
  stamp_polygon(x0y0 = wrap(n = 5, ncol = 3, height = 1.5),
                radius = .55, n = 7) +
  stamp_text(xy = wrap(n = 5, ncol = 3,
           height = 1.5), label = LETTERS[1:5])
```



---

`r flipbookr::chunk_reveal('stamp_segment_32', title = '### stamp_segment')`

```{r stamp_segment_32, include = F}
# segment on plot space
library(ggplot2)
ggplot(cars) +
 aes(speed, dist) +
 geom_point() +
 stamp_segment(color = "darkred",
 xend = 15, yend = 75)
```



---

`r flipbookr::chunk_reveal('stamp_segment_33', title = '### stamp_segment')`

```{r stamp_segment_33, include = F}
# segments on canvas
 ggcanvas() +
 stamp_segment(color = "green") +
 stamp_segment(x = 1:5, y = 2, xend = 2:6,
 size = 8, alpha = .5, lineend = "round")
```



---

`r flipbookr::chunk_reveal('stamp_spoke_34', title = '### stamp_spoke')`

```{r stamp_spoke_34, include = F}
# on canvas
 ggcanvas() +
 stamp_spoke(color = "green") +
 stamp_spoke(x = 2, y = 2, angle = pi * 1:8/4) +
 stamp_bubble(x = 2, y = 2, size = 15) +
 stamp_spoke(x = 1.5, y = 0, angle = pi * 1:50/50, alpha = 1:50/50) +
 stamp_text(x = 2, y = 2, label = "Hi!") +
 coord_equal() +
 theme_void()
```



---

`r flipbookr::chunk_reveal('stamp_spoke_35', title = '### stamp_spoke')`

```{r stamp_spoke_35, include = F}
# on plot
library(ggplot2)
ggplot(cars) +
 aes(speed, dist) +
 geom_point() +
 stamp_spoke(color = "darkred", radius = 25)
```



---

`r flipbookr::chunk_reveal('stamp_text_36', title = '### stamp_text')`

```{r stamp_text_36, include = F}
# cool text
library(ggplot2)
ggplot(cars) +
 aes(speed, dist) +
 geom_point() +
 stamp_text(label = stringr::str_wrap("a speed v. stopping distance, 1920s study tells us ...", 30),
            x = 12, y = 110,
            size = 5)
```



---

`r flipbookr::chunk_reveal('stamp_text_37', title = '### stamp_text')`

```{r stamp_text_37, include = F}
# some more
 ggcanvas() +
  stamp_text() +
  stamp_text(label = letters[1:4],
  xy = spoke(n = 4)) +
  stamp_text(x = 2) +
  scale_x_continuous(limits = c(-1,3)) +
  stamp_text(y = 1:2, x = 2,
             label = "Hellonthere!") +
  theme_void() +
  stamp_point(x = 1, y = 1,
              alpha = .4) +
  theme(plot.background =
       element_rect(fill = "seagreen",
       size = 0)) +
  scale_y_continuous(limits = c(-1,3))
```



---

`r flipbookr::chunk_reveal('stamp_tile_38', title = '### stamp_tile')`

```{r stamp_tile_38, include = F}
# on a canvas
ggcanvas() +
 stamp_tile(fill = "green") +
 stamp_tile(x = 1:5, y = 2, alpha = .8,
            fill = "steelblue",
            width = .95,
            size = 0) +
 coord_equal()
```



---

`r flipbookr::chunk_reveal('stamp_tile_39', title = '### stamp_tile')`

```{r stamp_tile_39, include = F}
# tile
library(ggplot2)
ggplot(cars) +
 aes(speed, dist) +
 geom_point() +
 stamp_tile(color = "red", x = 10,
            y = 90:100) +
 stamp_tile(height = 10,
            xy = spoke(x0 = 20, n = 15,
            radius = 6))
```



---

`r flipbookr::chunk_reveal('stamp_tile_40', title = '### stamp_tile')`

```{r stamp_tile_40, include = F}
# using a positioner
ggcanvas() +
 stamp_tile(xy = spoke())
```



---

`r flipbookr::chunk_reveal('wrap_png_41', title = '### wrap_png')`

```{r wrap_png_41, include = F}
ggcanvas() +
    stamp_png(x0y0 = wrap_png(n = 7)) +
    stamp_png(x0y0 = wrap_png(n = 5,
              y0 = -2.5), width = .85)
```



---

`r flipbookr::chunk_reveal('wrap_42', title = '### wrap')`

```{r wrap_42, include = F}
wrap()
wrap(n = 7, ncol = 2)
```


